Supporting Information

### 2020-07-17 manuscript/si.Rmd
Updates to analyses, SI, etc. Starting to reorganize analytical code.

\bleft
# Methods
## Mapping platform

@@

\clearpage
# Results

>>>>

\bleft
# Methods
## Assessing quality of composites
The rubric presented in Table 1 was used to assess the quality of the seasonal image composites. The imagery was evaluated by examining their Raster Foundry overlays within a `labeller` instance set up for the purpose.

```{r, echo=FALSE, message=FALSE}
library(kableExtra)
image_qual_criteria <- tibble(
  `Quality dimension` = c(
    "Percent affected by residual cloud", "Percent affected by cloud shadow", 
    "Number of visible scene boundaries", "Percent blurred"
  ),
  `3 pts` = c("<1%", "<1%", "None", "None"), 
  `2 pts` = c("1-5%", "1-5%", "1", "<20%"), 
  `1 pts` = c("5-10%", "5-10%", "2-3", "20-50%"),
  `0 pts` = c(">10%", ">10%", ">3", ">50%")
) 
cap <- glue::glue("Four dimensions used to assess the assess the quality
                  of the temporally composited image tiles, including the
                  criteria used to award points for scoring each dimension.")
kable(image_qual_criteria, format = "latex", booktabs = "T", caption = cap) %>% 
  kable_styling(full_width = TRUE, latex_options = c("hold_position")) %>% 
  column_spec(1, width = "8cm")
```

## Mapping platform

@@

\clearpage
# Results
## Image quality
